Tree establishment in models of forest dynamics: a key priority for further research

### 2023-02-02 manuscript/manuscriptRW.Rmd
changes in the M&M of the manuscript based on co-authors feedback

The simulation results were analyzed regarding the ingrowth levels
(i.e., ingrowth number per unit time and space), species composition of
the ingrowth, and ingrowth mortality. The observed data were modeled
using a Generalized Additive Model (GAM) with a negative binomial
distribution to better understand the trend and levels of the observed
ingrowth, relative to the simulation results per model. To avoid
overfitting we used the restricted maximum likelihood

@@

We evaluated the species composition across models and in relation to
the observed data by calculating the Shannon index based on the relative
frequency of the species in terms of basal area. The higher the value of
the index, the higher the species diversity at a particular site and
sample (Equation \ref{eqpiShannon}).

```{=tex}
\begin{equation}
H_n = - \sum_{i = 1}^{s}{p_{i}ln(p_{n,i})}\label{eqpiShannon}
\end{equation}
```
```{=tex}
\begin{equation}
p_{n,i} = \frac{r_{BA_{n,i}}}{Total_{BA_{n}}} \label{eqpiShannon2}
\end{equation}
```
where $s$ is the total number of species simulated that have ingrowth
basal area above zero in sample $n$; $p_{n,i}$ is the proportion of the
species $i$ calculated as the ingrowth basal area ($r_{BA_{n,i}}$) for
that species $i$ relative to the stand basal area ($Total_{BA_{n}}$) of
the sample $n$.

>>>>

The simulation results were analyzed regarding the ingrowth levels
(i.e., ingrowth number per unit time and space), species composition of
the ingrowth, and ingrowth mortality. The observed data were modeled
using a Generalized Additive Model [@wood2011] with a negative binomial
distribution and restricted maximum likelihood to better understand the
trend and levels of the observed ingrowth, relative to the simulation
results per model.

@@

We evaluated the species composition across models and in relation to
the observed data by calculating the Shannon index based on the relative
proportion of the species in terms of basal area. The higher the value
of the index, the higher the species diversity at a particular site and
sample (Equation \ref{eqpiShannon}).

```{=tex}
\begin{equation}
H_n = - \sum_{i = 1}^{s}{p_{n,i}ln(p_{n,i})}\label{eqpiShannon}
\end{equation}
```
```{=tex}
\begin{equation}
p_{n,i} = \frac{r_{BA_{n,i}}}{Total_{BA_{n}}} \label{eqpiShannon2}
\end{equation}
```
where $s$ is the total number of species simulated that have ingrowth
basal area above zero in sample $n$; $p_{n,i}$ is the proportion of the
species $i$ calculated as the ingrowth basal area ($r_{BA_{n,i}}$) for
that species $i$ relative to the stand basal area ($Total_{BA_{n}}$) of
the sample $n$.
